Kids SUMs Summary

### 2020-02-07 sums_summary.Rmd
small updates to SUMs functions

sums_filtered_date <- sums_clean %>% 
  mutate(sample_date = date_sums,
         sample_date = ymd(sample_date)) %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo_date, by = c("area", "home", "home_winter_id", "sample_date")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  ungroup() %>% 
  arrange(area, home)
```

@@

thresholds <- data %>% 
  mutate(datetime_sums = ymd_hms(datetime_sums)) %>% 
  group_by(area, home, winter_id) %>%
  mutate(threshold_temp = if_else(temp_c_sums >= temp, 1, 0),
         threshold_temp_event = if_else(threshold_temp == 1 & lag(threshold_temp) == 0, 
                                        "start", "Temp < threshold"),
         threshold_temp_event = if_else(is.na(threshold_temp_event), "start", threshold_temp_event),
         threshold_temp_event = if_else(threshold_temp == 1 & threshold_temp_event == "Temp < threshold",
                                      "Temp >= threshold", threshold_temp_event),
         threshold_temp_event = if_else(threshold_temp_event == "Temp >= threshold" &
                                      lead(threshold_temp_event) == "Temp < threshold", 
                                      "event", threshold_temp_event)) %>% 
  filter(threshold_temp_event == "event" | threshold_temp_event == "start") %>% 
  mutate(time_sums = as.character(time_sums),
         date_sums = as.character(date_sums)) %>%  
  spread(threshold_temp_event, datetime_sums) %>% 
  mutate(event = lead(event),
         time_diff_min = (event - start),
         time_diff_min = as.numeric(time_diff_min/60)) %>% 
  filter(!is.na(time_diff_min)) %>% 
  mutate(next_event = (lead(start)-event),
         next_event = as.numeric(next_event)/3600,
         event2 = if_else(next_event <= gap, lead(event), event),
         time_diff_min2 = (event - start),
         time_diff_min2 = as.numeric(time_diff_min2/60),
         event3 = if_else(next_event <= gap & lead(next_event) <= gap, lead(event, 2), event2),
         time_diff_min3 = (event3 - start),
         time_diff_min3 = as.numeric(time_diff_min3/60)) %>% 
  distinct(event3, .keep_all = TRUE) %>% 
  mutate(time_diff_min4 = (event3 - start),
         time_diff_min4 = as.numeric(time_diff_min4/60)) %>% 
  filter(!is.na(time_diff_min4)) %>% 
  group_by(area, home, winter_id, date_sums) %>% 
  summarize(n = n(), mean_time = mean(time_diff_min4))

>>>>

sums_filtered_date <- sums_clean %>% 
  mutate(sample_date = date_sums,
         sample_date = ymd(sample_date)) %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo_date, by = c("area", "home", "home_winter_id", "sample_date")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  ungroup() %>% 
  arrange(area, home)

sums_winter1_placebo <- sums_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  ungroup() %>% 
  arrange(area, home)
```

@@

thresholds <- data %>% 
  mutate(datetime_sums = ymd_hms(datetime_sums)) %>% 
  group_by(area, home, winter_id) %>%
  mutate(threshold_temp = if_else(temp_c_sums >= temp, 1, 0),
         threshold_temp_event = if_else(threshold_temp == 1 & lag(threshold_temp) == 0, 
                                        "start", "Temp < threshold"),
         threshold_temp_event = if_else(is.na(threshold_temp_event), "start", threshold_temp_event),
         threshold_temp_event = if_else(threshold_temp == 1 & threshold_temp_event == "Temp < threshold",
                                      "Temp >= threshold", threshold_temp_event),
         threshold_temp_event = if_else(threshold_temp_event == "Temp >= threshold" &
                                      lead(threshold_temp_event) == "Temp < threshold", 
                                      "event_end", threshold_temp_event)) %>% 
  filter(threshold_temp_event == "event_end" | threshold_temp_event == "start") %>% 
  mutate(time_sums = as.character(time_sums),
         date_sums = as.character(date_sums)) %>%  
  spread(threshold_temp_event, datetime_sums) %>% 
  mutate(event_end = lead(event_end),
         event_length_min = (event_end - start),
         event_length_min = as.numeric(event_length_min/60)) %>% 
  filter(!is.na(event_length_min)) %>% 
  mutate(hrs_till_next_event = (lead(start)-event_end),
         hrs_till_next_event = as.numeric(hrs_till_next_event)/3600,
         event_end2 = if_else(hrs_till_next_event <= gap, lead(event_end), event_end),
         event_end3 = if_else(hrs_till_next_event <= gap & lead(hrs_till_next_event) <= gap, 
                              lead(event_end, 2), event_end2),
         event_end4 = if_else(hrs_till_next_event <= gap & lead(hrs_till_next_event) <= gap
                              & lead(hrs_till_next_event, 2) <= gap, 
                              lead(event_end, 3), event_end3),
         event_end5 = if_else(hrs_till_next_event <= gap & lead(hrs_till_next_event) <= gap
                              & lead(hrs_till_next_event, 2) <= gap & lead(hrs_till_next_event, 3) <= gap, 
                              lead(event_end, 4), event_end4),
         event_end6 = if_else(hrs_till_next_event <= gap & lead(hrs_till_next_event) <= gap
                              & lead(hrs_till_next_event, 2) <= gap & lead(hrs_till_next_event, 3) <= gap
                              & lead(hrs_till_next_event, 4) <= gap, 
                              lead(event_end, 5), event_end5)) %>% 
  distinct(event_end6, .keep_all = TRUE) %>% 
  mutate(event_length_min = (event_end6 - start),
         event_length_min = as.numeric(event_length_min/60),
         hrs_till_next_event = (lead(start)-event_end),
         hrs_till_next_event = as.numeric(hrs_till_next_event)/3600) %>% 
  filter(!is.na(event_length_min)) %>% 
  group_by(area, home, winter_id, date_sums) %>% 
  summarize(n = n(), mean_time = mean(event_length_min))
